COW/CALF:
currently tag
$4.21 1-49               
$2.90 50-99
$2.73 100-499
$2.43 500-999
$2.42 1000-1999
$2.43 2000-4999
$2.40 5,000+

Here we get a conservative estimate (upper bound). We take the weighted mean of the about to get one number. 

```{r}
cost_CowCalf_Tag <- weighted.mean(x = c(4.21, 2.90, 2.73, 2.43, 2.42, 2.43, 2.40), w = c(50,99,499,999,1999,4999,5000))
```

currently not tag
$5.54
$5.29
$5.20
$5.04
$5.04
$5.04
$5.04

```{r}
cost_CowCalf_NTag <- weighted.mean(x = c(5.54, 5.29, 5.20, 5.04, 5.04, 5.04, 5.04), w = c(50,99,499,999,1999,4999,5000))
```


BACKGROUND:

$0.75  31
$0.43  104
$0.22  345
$0.19  496
$0.20  722
$0.16  1,453
$0.14  2,963



```{r}
cost_Bckg <- weighted.mean(x = c(0.75, 0.43, 0.22, 0.19, 0.20, 0.16, 0.14), w = c(31,104,345,496,722,1453,2963))
```

FEEDLOT:

$0.50  1-999
$0.16  1000-1999
$0.14  2000-3999
$0.12  4000-7999
$0.12  8000-15999
$0.12  16000-31999
$0.12  32000+

```{r}
cost_Feedlot <- weighted.mean(x = c(0.50, 0.16, 0.14, 0.12, 0.12, 0.12, 0.12), w = c(999,1999,3999,7999,15999,31999,32000))
```

PACKERS:

$0.47   300
$0.16   1.3 million

```{r}
cost_Packers <- weighted.mean(x = c(0.47,0.16), w = c(300,1.3*1000000))
```



Aggregating all the costs. I am using the upperbound from the cow/calf costs i.e., the costs from the operations that currently not tag

```{r}
total_Costs <- sum(cost_CowCalf_NTag, cost_Bckg, cost_Feedlot, cost_Packers)
```











#### Some of my concerns:

How am I going to change the quantities? 
Am I going to keep the observed supply and demand?
Keep the demand same but change the supply?
We know the share depends on ps & pc, so if it changes the sl and cl supply changes as well.

Is it okay to increase costs for every year?
    As soon as the costs are increased the supply should change immediately?
      Ans: Supply of what? 
              Fed cattle meat could decrease (if the producer expexts a high demand this would definitly happen, 
                                                through adding more heifers to the breeding stock.)
              Cull cow meat could increase (If we keep a cow for one more year, costs associated with that animal and 
                                              it's progeny would increase.)
                                              
                                              
                                              
#### One thought:
After estimating $\tilde{\mu}$ and $\tilde{s}$, compute the share, $\hat{sl}$, $\hat{cl}$, and $\hat{demand}$ again? (because I am seeing no change in $\hat{sl}$).

This is not working. $\hat{sl}$ remains same, $\hat{demand}, \hat{cl}$ change by a little. Not a huge difference.




### Some prelim results:
* The prices and costs are changing by a small magnitude (very small! we are speaking of single digit dollars per cwt)
* The quantities remain same! (because the prices change by very small magnitude).







